### 2019-05-29 2-Chapters/2-Chapter/chapter2.tex
I need to shower

In this Section, we start by discussing two naive strategies which fail dramatically.
%
We then expose two simple strategies, which performs efficiently only if they are tuned using a prior knowledge of the problem difficulty, but are thus unusable for practical applications.
%
We continue by presenting a first efficient policy, \UCB, that uses upper confidence bounds (UCB) on the mean estimates, and is known to be order-optimal for bounded rewards.
Two other well-known and optimal algorithms are exposed: \klUCB{} extends the idea of \UCB{} but use smaller confidence intervals and thus typically has better theoretical results, and Thompson sampling which takes a Bayesian point-of-view instead of relying on the principle of optimism in the face of uncertainty.
%
Finally, we conclude this Section by briefly exposing other families of algorithms.

@@

% ---------------------------------------------------
\paragraph{Naive strategies: pure exploitation or pure exploration}

@@

Using the same analysis, if a lower-bound $d$ on the positive gaps is known beforehand, one can find a tuning of $T_0$ that gives a logarithmic regret.
%
Like for the lower-bound, we have $R_T \leq (\max_{k: \Delta_k > 0} \Delta_k) T_0 + p (T - T_0)$, thus $R_T \leq K T_0 + K \exp(-T_0 d^2/4) T$ using Hoeffding's inequality again. Optimizing on $T_0$ gives $T_0 = 4/d^2 \log(d^2 T / 4)$
and proves that the ``explore-then-exploit'' strategy can also obtain an order-optimal regret, $R_T \leq K 4/d^2 (1 + \log(d^2 T / 4)) = \bigO{\log(T)}$, if it is tuned with a fixed time $T_0$ using prior knowledge on the problem (\ie, $d$) and the horizon $T$.
%
This strategy is also referred to as ``explore-first'', it can also achieve $R_T = \bigO{T^{2/3} (K \log(T))^{1/3}}$ without prior knowledge on the problem, as shown in Section~1 of \cite{Slivkins2019}.

@@

\TODOL{Expliquer UCB}
\TODOL{Expliquer que les indices UCB = des UCB sur les moyennes + principle of optimism in face of uncertainty}
Optimism in face of uncertainty, for UCB etc.
$\UCB_1$ from \cite{Auer02}, using $\alpha=1$ (\texttt{UCBalpha}).
It achieves order-optimal problem-dependent bounds with a $\cO(K\log(T)/\Delta^2)$ regret.

compute the index $U_k(t) = \widehat{\mu_k}(t) + \sqrt{\alpha \log(t) / N_k(t)}$.

The \UCB{} indexes are computed as follows:
\begin{align}\label{eq:UCB_index}
    \forall k,\;\;\;
    U_k^{\UCB}(t) = \sup\limits_{q \in [a, b]} \left\{ q : \mathrm{kl}(\frac{X_k(t)}{N_k(t)}, q) \leq \frac{c \log(t)}{N_k(t)} \right\}.
\end{align}

@@

If rewards lie in $[a,b]$, then the indexes are computed as follows:
\begin{align}\label{eq:klUCB_index}
    \forall k,\;\;\;
    U_k^{\klUCB}(t) = \sup\limits_{q \in [a, b]} \left\{ q : \mathrm{kl}(\frac{X_k(t)}{N_k(t)}, q) \leq \frac{c \log(t)}{N_k(t)} \right\}.
\end{align}

@@

Many variants have been proposed in the multi-armed bandits literature.
For instance, \UCB-H (and \klUCB-H) replaces the $\log(t)$ by a $\log(T)$, and it corresponds to the first algorithm analyzed in \cite{Auer02}.
Using an estimator for the variance leads to \UCB-V, efficient for instance for problems where the arms are Gaussian distributions with unknown variance.
Other variants include \UCB$^+$, \UCB-dagger from \cite{Lattimore2018refining}, {\UCB}oost, and many more.
%
They are usually comparable to the original \UCB{} algorithm, in terms of time and memory complexity, and achieves improved regret upper bounds in the same setting or extension of the initial setting.

\paragraph{Other policies inspired by \UCB}
%
The ``Successive Elimination'' policy also uses confidence bounds, and use both UCB and Lower Confidence Bounds (LCB). After playing each active arms once, it eliminates arm $a$ if it is statistically safe that it is sub-optimal, \ie, if there is another arm $a' \neq a$ such that $\UCB_a(t) < \mathrm{LCB}_{a'}(t)$.
It also achieves a $\bigO{\log(T)}$ problem-dependent regret upper bound, and a $\bigO{\sqrt{K T \log(T)}}$ problem-independent bound.

@@

Thompson sampling is the oldest known MAB algorithms, dating back from the first paper by Thompson in 1933 \cite{Thompson33}.
It became popular since its asymptotical and finite-time analyses in \cite{AgrawalGoyal11,Kaufmann12Thompson}.
%
Thompson sampling uses a Bayesian point of view:
instead of building confidence intervals on the means of the arms like \UCB{} does,
it starts with a prior on the $K$ distributions (\eg, a flat uniform prior), and then after every observation $(k, r(t))$ it updates the posterior distribution of the arm $k$ with a new data $r(t)$.
If $\pi_k(t)$ denotes this posterior distribution, Thompson sampling makes its decision at time $t$ by first sampling a random sample $s_k \sim \pi_k(t)$, and then playing according to the ``optimism in face of uncertainty'' philosophy if these samples represent the arms (expected) quality: $C(t) \in \argmax_k s_k$.

For problems with Bernoulli distributions on the $K$ arms,
the best choice of prior is a Beta distribution, that starts as an initially uniform prior (\ie, $\mathrm{Beta}(1,1)$),
and maintain a distribution $\mathrm{Beta}(X_k(t)+1,N_k(t)-X_k(t)+1)$ after $X_k(t)$ successes observed on arm $k$ and $N_k(t)-X_k(t)$.
We detail the Thompson sampling algorithm in this case, below in Algorithm~\ref{algo:2:ThompsonSampling}, as it corresponds to the case used in Chapter~\ref{chapter:4} in Section~\ref{sub:41:numericalResults}.
%
In this setting as well as for Gaussian distributions,
Thompson sampling was proved to achieve asymptotical optimal problem-dependent bounds \cite{Kaufmann12Thompson,AgrawalGoyal11}.

@@

For curiosity, we mention a third Bayesian algorithm, AdBandits introduced in \cite{Truzzi13}, mainly because it has not gained any popularity despite its good empirical performance.
%  using $\alpha=1$ (\texttt{AdBandits}).
AdBandits follows the same assumptions as Thompson sampling and Bayes-UCB, and for instance for Bernoulli problems it uses a Beta posterior on each arm.
It uses a random mixture between the two algorithms, and with a certain probability it uses the Thompson sampling decision rule, otherwise it uses the Bayes-UCB decision rule.
It was proposed in this article \cite{Truzzi13} and illustrated on empirical simulations, but no theoretical analysis was given.
%  and it did not gain popularity since then.
% In practice, AdBandits is usually (slighly) more efficient than both Thompson sampling and Bayes-UCB in terms of regret, it is comparable in terms of computation times, but costs more memory.

Finally, we would like to mention that a recent work \cite{KimTewari2019} presented an approach that closes the gap between the principle of optimism in the face of uncertainty and the Bayesian point-of-view.
%  underlying the approaches based on UCB, might not be necessary at all.
% With perturbation: maybe we don't need optimism in face of uncertainty, we just need uniform sampling!
The authors of \cite{KimTewari2019} showed that their Randomized Confidence Bound (RCB) algorithm can achieve the same regret upper bounds as \UCB{} or Thompson sampling, with uniform perturbations.
Their RCB algorithm ressembles \UCB, and builds the same confidence intervals $\mathrm{LCB}_k(t), \UCB_k(t)$ on arm $k$ at time $t$. But instead of playing the arm with maximum UCB, a random sample is taken on each interval, and the played arm is the one maximizing this sample.
% https://smpybandits.github.io/docs/Policies.RandomizedIndexPolicy.html

@@

We briefly mention other families of policies.

@@

Another important family of bandits algorithms are the algorithms proposed for the adversarial setting \cite{Auer02NonStochastic}.
The first of them is the Exp3 policy, for ``\emph{Exp}onential weights for \emph{Exp}loitation and \emph{Exp}loiration'',
which is an example of the well-known \emph{multiplicative weights update algorithm}\footnote{~For more details see
the Wikipedia \href{https://en.wikipedia.org/wiki/Multiplicative_weight_update_method}{\texttt{en.wikipedia.org/wiki/Multiplicative\_weight\_update\_method}},
or this blog post by Jeremy Kun \href{https://jeremykun.com/2017/02/27/the-reasonable-effectiveness-of-the-multiplicative-weights-update-algorithm/}{\texttt{JeremyKun.com/2017/02/27/the-reasonable-effectiveness-of-the-}}\\
\href{https://jeremykun.com/2017/02/27/the-reasonable-effectiveness-of-the-multiplicative-weights-update-algorithm/}{\texttt{multiplicative-weights-update-algorithm}},
which comes with an interactive online demonstration to help understanding the behavior of the algorithm, hosted at \href{https://j2kun.github.io/mwua/index.html}{\texttt{j2kun.GitHub.io/mwua/}} (accessed the 24th of May 2019). More details can be found in the survey \cite{Arora2012multiplicative}.},
a family of algorithms developed since the 1950s, and applied to a wide range of different domains.
% https://smpybandits.github.io/docs/Policies.Exp3.html
%
The Exp3 policy maintains weights $w_k(t)$ on the $K$ arms, and at time $t$ it samples an arm from the distribution which is a mixture of $\bm{w}(t)=[w_1(t),\dots,w_K(t)]$ and the uniform distribution:
$\Pr(C(t)=k) = (1-\gamma) w_k(t) + \gamma \frac{1}{K}$.
The weights are initially uniform, \ie, $w_k(0)=\frac{1}{K}$, and then at each time after observing a reward $r_k(t)$ from arm $k$, Exp3 updates the weight of the chosen arm multiplicatively, using $w_k(t+1) = w_k(t) \times \exp(\widehat{r_k}(t) / (\gamma N_k(t)))$. The weights are then renormalized, the have a sum $\sum_k w_k(t+1) = 1$.
This notation $\widehat{r_k}(t)$ means an unbiased estimator of the reward $r_k(t)$, that is, $\widehat{r_k}(t) = \Pr(C(t)=k)$.
%
Like for the $\varepsilon$-greedy policy, the parameter $\gamma$ can be constant, or can be a decreasing sequence $(\gamma_t)_t$.
%
It was proved in \cite{Auer02NonStochastic} that Exp3 with constant temperature parameter $\gamma$ achieves $R_T = \bigO{\sqrt{K T \log(T)}}$ problem-independent regret,
while using a decreasing sequence, such as $\gamma_t = \sqrt{\log(K) / K} \log(t) / t$ gives an order-optimal problem-independent regret upper-bound of $\bigO{\sqrt{K T}}$.
For a short proof of this results as well as more details on Exp3, see \cite{Bubeck12}.

% https://smpybandits.github.io/docs/Policies.Exp3PlusPlus.html
Finally, it is worth mentioning the Exp3$^{++}$ algorithm, as a recent variant of Exp3, proposed by \cite{Seldin17},
that uses an adaptive tuning of its parameters.
It is anytime, and was proven to obtain good ``best of both world'' performances, meaning that it achieves $\cO(K\log(T)/\Delta^2)$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.

@@

As explained before, in the last few years, the MAB research community has been interested in finding algorithms which achieves both a problem-dependent logarithmic and a minimax upper-bounds.
The first example is MOSS from \cite{Audibert2009minimax}, or recently \KLUCBpp{} in \cite{Menard17}.
They are both index-based, using the following indexes:
\begin{align}\label{eq:2:indexes_for_MOSS_klUCBpp}
    \forall k,\;\;\;
    U^{\mathrm{MOSS}}_k(t) &= \frac{X_k(t)}{N_k(t)} + \sqrt{\max\left(0, \frac{\log\left(\frac{t}{K N_k(t)}\right)}{N_k(t)}\right)}. \\
    \forall k,\;\;\;
    U^{\KLUCBpp}_k(t) &= \sup\limits_{q \in [a, b]} \left\{ q : \mathrm{kl}(\hat{\mu}_k(t), q) \leq \frac{c g(N_k(t), T, K)}{N_k(t)} \right\}.
\end{align}
%
If we denote $g(t, T, K) = \log^+(y (1 + \log^+(y)^2))$, and $y = \frac{T}{K t}$, where $\log^+(x) = \max(0, \log(x))$.

@@

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proved to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses a modified version of the indexes of the \klUCB$^+$ algorithm, for arms that are not sampled much, and a modified version of the indexes of the MOSS$^+$ algorithm, for the other arms.
To detail this, first let $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch use the index defined as follows:
%
\begin{align}\label{eq:2:indexes_for_klUCBswitch}
    U^{\mathrm{MOSS}+}_k(t) &= \frac{X_k(t)}{N_k(t)} + \sqrt{\max\left(0, \frac{\log\left(\frac{T}{K N_k(t)}\right)}{N_k(t)}\right)}. \\
    U^{\KLUCB+}_k(t) &= \sup\limits_{q \in [a, b]} \left\{ q : \mathrm{kl}(\hat{\mu}_k(t), q) \leq \frac{c \log(T / (K * N_k(t)))}{N_k(t)} \right\} \\
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) &= \begin{cases}
        U^{KL+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{MOSS+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align}

>>>>

This Section starts by discussing two naive strategies which fail dramatically,
%
and then we present two simple strategies which performs efficiently, only if they are tuned using a prior knowledge of the problem difficulty, but are thus unusable for practical applications.
%
We focus then on index policies, with a first efficient policy, \UCB, that uses upper confidence bounds (UCB) on the means estimates, and is known to be order-optimal for bounded rewards.
Two other well-known and optimal algorithms are exposed: \klUCB{} extends the idea of \UCB{} but use smaller confidence intervals and thus it typically obtains better theoretical results, and Thompson sampling which replaces the principle of ``optimism under uncertainty'' by a Bayesian point-of-view.
%
Finally, we conclude by briefly exposing other families of algorithms.

@@

% ---------------------------------------------------
\subsection{Naive or simple strategies}
\label{sub:2:naiveSimpleStrategies}

\paragraph{Naive strategies: pure exploitation or pure exploration}

@@

Using the same analysis, if a lower-bound $d$ on the positive gaps is known beforehand, one can find a tuning of $T_0$ that gives a logarithmic regret.
%
Like for the lower-bound, we have $R_T \leq (\max_{k: \Delta_k > 0} \Delta_k) T_0 + p (T - T_0)$, thus $R_T \leq K T_0 + K \exp(-T_0 d^2/4) T$ using Hoeffding's inequality again. Optimizing on $T_0$ gives $T_0 = 4/d^2 \log(d^2 T / 4)$
and proves that the ``explore-then-exploit'' strategy can also obtain an order-optimal regret, $R_T \leq K 4/d^2 (1 + \log(d^2 T / 4)) = \bigO{\log(T)}$, if it is tuned with a fixed time $T_0$ using prior knowledge on the problem (\ie, $d$) and the horizon $T$.
%
This strategy can also achieve $R_T = \bigO{T^{2/3} (K \log(T))^{1/3}}$ without prior knowledge on the problem, as shown in Section~1 of \cite{Slivkins2019}.

@@

Let us consider another approach for adaptive exploration, known as ``optimism under uncertainty'': assume each arm is as good as it can possibly be given the observations so far, and choose the best arm based on these optimistic estimate.
%
This intuition leads to the $\UCB_1$ algorithm, initially introduced in \cite{Auer02}.
For a parameter $\alpha$, the \UCB{} indexes are computed as follows, as a sum of
the \emph{average reward} $\widehat{\mu_k}(t)=\frac{X_k(t)}{N_k(t)}$
and a \emph{confidence radius} $\xi_k(t) = \sqrt{\alpha \frac{\log\left(t\right)}{N_k(t)}\right)}$.
%
\begin{align}\label{eq:UCB_index}
    U_k^{\UCB}(t) = \underbrace{\frac{X_k(t)}{N_k(t)}}_{\widehat{\mu_k}(t)} + \underbrace{\sqrt{\alpha \frac{\log\left(t\right)}{N_k(t)}\right)}}_{\xi_k(t)}.
\end{align}

This selection rule makes sense for the following reason:
an arm $k$ is chosen at step $t$ because it has a large $U_k^{\UCB}(t) = \UCB_k(t)$, which can happen for two reasons:
$i)$ because the average reward $\widehat{\mu_k}(t)$ is large, in which case this arm is likely to have a high reward,
$ii)$ and/or because the confidence radius $\xi_k(t)$ is large, in which case this arm has not been explored much.
Either reason makes this arm worth choosing.
%
Furthermore, these two terms $\widehat{\mu_k}(t)$ and $\xi_k(t)$ in the \UCB{}  respectively represent exploitation and exploration, and summing them up is a natural way to trade off the two.
The parameter $\alpha$ in $\xi_k(t)$ also controls this trade-off, and the theoretical analysis suggests to restrict to $\alpha\geq1/2$, and to chose $\alpha=1/2$ for optimal uniform performance.

To analyze the algorithm $\UCB_1$, we denote again $k^*$ an optimal arm, and $C(t)$ is the arm chosen by the algorithm in round $t$.
According to the algorithm, $\UCB_k(t) \geq \UCB_{k^*}(t)$.
%
Under the clean event,μ(at) +rt(at)≥ ̄μt(at)andUCBt(a∗)≥μ(a∗). Therefore:
XXX
It follows that
XXX

More details on the proofs can be found for instance in Chapter~2 of \cite{Bubeck12}, or Section~1.3 of \cite{Slivkins2019}.
% \TODOL{Expliquer la fin}
The $\UCB_1$ algorithm achieves order-optimal problem-dependent bounds with a $\cO(K\log(T)/\Delta^2)$ regret.

It has the advantage of not relying on any prior knowledge of the problem difficulty, of being anytime, and computationally simple, for both memory and time aspects.
The $\UCB_1$ algorithm requires a constant storage capacity for each arm (storing $X_k(t)$ and $N_k(t)$ require two integers or a \texttt{float} and an integer, \ie, $\bigO{1}$), giving a storage capacity of $\bigO{K}$, independently of the horizon $T$.
It also needs to perform some mathematical operations, but a square-root and a logarithm are cheap, thus it costs a $\bigO{1}$ constant time for each arm and time step, thus a time $\bigO{K T}$ for the $T$ rounds.
%
We use it as the base building block for other policies in Chapter~\ref{chapter:4}, for these reasons.
Moreover, the $\UCB_1$ algorithm has the advantage of being easy to explain and understand, and its decisions can be interpreted clearly: by reading the values of $\widehat{\mu_k}(t)$ and $\UCB_k(t)$, anyone can see why an arm was chosen at anytime.
This is why it is used in our demonstration presented in Section~\ref{sec:4:gnuradio}.

@@

If rewards lie in $[a,b]$, then the indexes are computed as follows:
\begin{align}\label{eq:klUCB_index}
    U_k^{\klUCB}(t) = \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{c \log(t)}{N_k(t)} \right\}.
\end{align}

@@

Many variants of the \UCB{} algorithms have been studied in the multi-armed bandits literature.
For instance, \UCB-H replaces the $\log(t)$ by a $\log(T)$ (as well as \klUCB-H), and it actually corresponds to the first algorithm analyzed in \cite{Auer02}.
Using an estimator for the variance of the arms' samples gives \UCB-V, which was for instance proven to be efficient against Gaussian distributions with unknown variance.
Other variants include \UCB$^+$, $\UCB^{\dagger}$ from \cite{Lattimore2018refining}, {\UCB}oost, and many more.
%
All these variants are usually comparable to the original \UCB{} algorithm, in terms of time and memory complexity, and they achieve improved regret upper bounds in the same setting or some extensions of the initial setting.

\paragraph{Other policies inspired by \UCB}
%
The ``Successive Elimination'' policy also uses confidence bounds, and use both Upper and Lower Confidence Bounds (LCB).
After playing each active arms once, it eliminates arm $a$ if it is statistically identified as sub-optimal, \ie, if there is another arm $a' \neq a$ such that $\UCB_a(t) < \mathrm{LCB}_{a'}(t)$.
It also achieves a $\bigO{\log(T)}$ problem-dependent regret upper bound, and a $\bigO{\sqrt{K T \log(T)}}$ problem-independent bound.

@@

Thompson sampling is the oldest known MAB algorithms, dating back from the first paper by Thompson in 1933 \cite{Thompson33}.
It became popular since its asymptotical and finite-time analyses in \cite{AgrawalGoyal11,Kaufmann12Thompson}.
%
Thompson sampling uses a Bayesian point of view:
instead of building confidence intervals on the means of the arms like \UCB{} does,
it starts with a prior on the $K$ distributions (\eg, a flat uniform prior), and then after every observation $(k, r(t))$ it updates the posterior distribution of the arm $k$ with a new data $r(t)$.
If $\pi_k(t)$ denotes this posterior distribution, Thompson sampling makes its decision at time $t$ by first sampling a random sample $s_k \sim \pi_k(t)$, and then playing according to the ``optimism under uncertainty'' philosophy if these samples represent the arms (expected) quality: $C(t) \in \argmax_k s_k$.

For problems with Bernoulli distributions on the $K$ arms,
the best choice of prior is a Beta distribution, that starts as an initially uniform prior (\ie, $\mathrm{Beta}(1,1)$),
and maintain a distribution $\mathrm{Beta}(X_k(t)+1,N_k(t)-X_k(t)+1)$,
as $X_k(t)$ counts the number of successes observed on arm $k$, and $N_k(t)-X_k(t)$ counts the number of failures.
%
We detail the Thompson sampling algorithm in this case, below in Algorithm~\ref{algo:2:ThompsonSampling}, as it corresponds to the case used in Chapter~\ref{chapter:4} in Section~\ref{sub:41:numericalResults}.
%
In this setting as well as for Gaussian distributions,
Thompson sampling was proven to achieve asymptotical optimal problem-dependent bounds \cite{Kaufmann12Thompson,AgrawalGoyal11}.

@@

For curiosity, we mention a third Bayesian algorithm, AdBandits introduced in \cite{Truzzi13}, mainly because it has not gained any popularity despite its good empirical performance.
%  using $\alpha=1$ (\texttt{AdBandits}).
AdBandits follows the same assumptions as Thompson sampling and Bayes-UCB, and for instance for Bernoulli problems it uses a Beta posterior on each arm.
It uses a random mixture between the two algorithms, and with a certain probability it uses the Thompson sampling decision rule, otherwise it uses the Bayes-UCB decision rule.
It was proposed in this article \cite{Truzzi13} and illustrated on empirical simulations, but no theoretical analysis was given.
We found that in practice it can achieve very good performance, as illustrated in Section~\ref{sec:3:reviewSPAlgorithms}.
%  and it did not gain popularity since then.
% In practice, AdBandits is usually (slighly) more efficient than both Thompson sampling and Bayes-UCB in terms of regret, it is comparable in terms of computation times, but costs more memory.

Finally, we would like to mention that a recent work \cite{KimTewari2019} presented an approach that closes the gap between the principle of optimism under uncertainty and the Bayesian point-of-view.
%  underlying the approaches based on UCB, might not be necessary at all.
% With perturbation: maybe we don't need optimism in face of uncertainty, we just need uniform sampling!
The authors of \cite{KimTewari2019} showed that their Randomized Confidence Bound (RCB) algorithm can achieve the same regret upper bounds as \UCB{} or Thompson sampling, with uniform perturbations.
Their RCB algorithm ressembles \UCB, and builds the same confidence intervals $\mathrm{LCB}_k(t), \UCB_k(t)$ on arm $k$ at time $t$. But instead of playing the arm with maximum UCB, a random sample is taken on each interval, and the played arm is the one maximizing this sample.
% https://smpybandits.github.io/docs/Policies.RandomizedIndexPolicy.html

@@

We can briefly mention other families of policies.

@@

Another important family of bandits algorithms are the algorithms proposed for the adversarial setting \cite{Auer02NonStochastic}.
The first of them is the Exp3 policy, for ``\emph{Exp}onential weights for \emph{Exp}loitation and \emph{Exp}loiration'',
which is an example of the well-known \emph{multiplicative weights update algorithm}\footnote{~For more details see
on Wikipedia \href{https://en.wikipedia.org/wiki/Multiplicative_weight_update_method}{\texttt{en.wikipedia.org/wiki/Multiplicative\_weight\_update\_method}},
or this blog post by Jeremy Kun \href{https://jeremykun.com/2017/02/27/the-reasonable-effectiveness-of-the-multiplicative-weights-update-algorithm/}{\texttt{JeremyKun.com/2017/02/27/the-reasonable-effectiveness-of-the-}}\\
\href{https://jeremykun.com/2017/02/27/the-reasonable-effectiveness-of-the-multiplicative-weights-update-algorithm/}{\texttt{multiplicative-weights-update-algorithm}},
which comes with an interactive online demonstration to help understanding the behavior of the algorithm, hosted at \href{https://j2kun.github.io/mwua/index.html}{\texttt{j2kun.GitHub.io/mwua/}} (accessed the 24th of May 2019). More details can be found in the survey \cite{Arora2012multiplicative}.},
a family of algorithms developed since the 1950s, and applied to a wide range of different domains.
% https://smpybandits.github.io/docs/Policies.Exp3.html
%
The Exp3 policy maintains weights $w_k(t)$ on the $K$ arms, and at time $t$ it samples an arm from the distribution which is a mixture of $\bm{w}(t)=[w_1(t),\dots,w_K(t)]$ and the uniform distribution:
$\Pr(C(t)=k) = (1-\gamma) w_k(t) + \gamma \frac{1}{K}$.
The weights are initially uniform, \ie, $w_k(0)=\frac{1}{K}$, and then at each time after observing a reward $r_k(t)$ from arm $k$, Exp3 updates the weight of the chosen arm multiplicatively, using $w_k(t+1) = w_k(t) \times \exp(\widehat{r_k}(t) / (\gamma N_k(t)))$. The weights are then renormalized, the have a sum $\sum_k w_k(t+1) = 1$.
This notation $\widehat{r_k}(t)$ means an unbiased estimator of the reward $r_k(t)$, that is, $\widehat{r_k}(t) = \Pr(C(t)=k)$.
%
Like for the $\varepsilon$-greedy policy, the parameter $\gamma$ can be constant, or can be a decreasing sequence $(\gamma_t)_t$.
%
It was proved in \cite{Auer02NonStochastic} that Exp3 with constant temperature parameter $\gamma$ achieves $R_T = \bigO{\sqrt{K T \log(T)}}$ problem-independent regret,
while using a decreasing sequence, such as $\gamma_t = \sqrt{\log(K) / K} \log(t) / t$ gives an order-optimal problem-independent regret upper-bound of $\bigO{\sqrt{K T}}$.
For a short proof of this results as well as more details on Exp3, see \cite{Bubeck12}.
%
% https://smpybandits.github.io/docs/Policies.Exp3PlusPlus.html
Finally, it is worth mentioning the Exp3$^{++}$ algorithm, as a recent variant of Exp3, proposed by \cite{Seldin17},
that uses an adaptive tuning of its parameters.
It is anytime, and was proven to obtain good ``best of both world'' performances, meaning that it achieves $\cO(K\log(T)/\Delta^2)$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.

@@

As explained before, in the last few years, the MAB research community has been interested in finding algorithms which achieves both a problem-dependent logarithmic and a minimax upper-bounds.
The first example is MOSS from \cite{Audibert2009minimax}, or recently \KLUCBpp{} in \cite{Menard17}.
They are both index-based, using the following indexes:
\begin{align}\label{eq:2:indexes_for_MOSS_klUCBpp}
    U^{\mathrm{MOSS}}_k(t) &= \frac{X_k(t)}{N_k(t)} + \sqrt{\max\left(0, \frac{\log\left(\frac{t}{K N_k(t)}\right)}{N_k(t)}\right)}. \\
    U^{\KLUCBpp}_k(t) &= \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{g(N_k(t), T, K)}{N_k(t)} \right\}.
\end{align}
%
If we denote $g(t, T, K) = \log^+(y (1 + \log^+(y)^2))$, and $y = \frac{T}{K t}$, where $\log^+(x) = \max(0, \log(x))$.

@@

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proved to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses a modified version of the indexes of the \klUCB$^+$ algorithm, for arms that are not sampled much, and a modified version of the indexes of the MOSS$^+$ algorithm, for the other arms.
To detail this, first let $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch use the index defined as follows:
%
\begin{align}\label{eq:2:indexes_for_klUCBswitch}
    U^{\mathrm{MOSS}+}_k(t) &= \frac{X_k(t)}{N_k(t)} + \sqrt{\max\left(0, \frac{\log\left(\frac{T}{K N_k(t)}\right)}{N_k(t)}\right)}. \\
    U^{\KLUCB+}_k(t) &= \sup\limits_{q \in [a, b]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \frac{\log(T / (K N_k(t)))}{N_k(t)} \right\} \\
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) &= \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align}
